\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage[letterpaper, margin=1in]{geometry}

\pagestyle{plain}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\begin{document}
\selectlanguage{english}

\begin{Minutes}{Initial Team Meeting}
\participant{\
    Emily Shepherd, \
    Mohit Gupta, \
    Dan Playle, \
    Toby Finch, \
    Calin Pasat}
\minutesdate{30 September 2015}
\starttime{16:00}
\endtime{16:30}
\location{Zepler Level 2 Labs}
\maketitle

\topic{Project Brief}
The team agreed to that the brief was appropriate; no-one had any proposed changes. Emily suggested using the initial brief with little alteration.

\task{Emily}{Write Brief}

\topic{Subteams}
This section was led by Dan - the group first attempted to identify the key sections of the
task, agreeing quickly that these were:
\begin{itemize}
	\item Designing the algorithm
	\item Implementing the algorithm in embedded C
	\item System Verilog
\end{itemize}

System Verilog was discussed first, with Dan, Mohit and Calin stating
they had experience with this. Emily and Toby stated that they had
none. Next, Dan informed the group that he had worked with Embedded C before; Emily
said she had good experience with C although not in an embedded context,
however she was keen to give it a try. Finally, the team discussed the designing
algorithm itself from an abstract perspective - Toby and Emily were both eager to be involved in this aspect.

\decision*{Designing the algorithm - Toby and Emily}
\decision*{Implementing the algorithm in embedded C - Emily and Dan}
\decision*{System Verilog - Dan, Mohit and Calin}

\topic{Team Roles}
Emily reminded the group that Dr Merrett had recommended roles to be
decided upon. Dan noted that the job of leader and minute taker could
most likely be performed by one person. Calin quickly volunteered as
Budget Holder, citing prior
experience with a previous project. Toby said he would be happy to act as
the Company Representative. Finally, Emily put herself forward as Leader
and Minute Taker, stating that she enjoys writing minutes. The team were
unanimously happy with these appointments.

\decision*{Leader - Emily}
\decision*{Budget Holder - Calin}
\decision*{Company Representative - Toby}

\topic{Tools}
Dan asked which communication tool the team would like to use and put
forward Slack\footnote{https://slack.com/} as an option. The team were unfamiliar with this, so Dan
explained that it is a Skype-like tool, which has good support on a
variety of devices, including mobiles. Emily asked if it allowed any
structured chat - Dan confirmed that it was possible to make sub-groups
and summarised it as a "friendlier IRC".

Emily suggested using Git version control software, to which to team
agreed. Mohit asked if this would be hosted on GitHub or elsewhere. Emily
said that she liked GitHub but it might be more appropriate to use ECS'
in-house Git host: SourceKettle. Mohit queried whether we would need to be
on ECS' network in order to access this. Emily said she did not believe so,
although she was not sure. Dan pointed out that other teams had had
problems with this in the past. The team agreed GitHub was the most
sensible option.

Dan then stated that he has a strong preference for the report to be
written in LaTeX which the majority of the team were happy with. Emily expressed a dislike
for LaTeX but stated she was happy to use it for this project. Toby noted
that, while he had used LaTeX before, he is not particularly well-versed
with it.

\decision*{Use Slack for team Communication}
\decision*{Keep all reports, minutes and code under Git verion control, hosted on GitHub}
\decision*{Use LaTeX for reports and minutes}

\topic{Ethics and Best Practice}
Emily brought up the question of Ethics approval - Dan asked if anyone
had any experience with the ethics committee process to which the group
unanimously answered no. Emily, however, stated that she had been in
contact with the Research Governance Board in the past, so volunteered to
take the lead in the ethics process. At this point a PhD student
approached and informed the meeting that the ethics process is quicker in
the first few weeks rather than later; as such the group agreed to do this as a priority.

Emily asked where the group planned to find subjects for the tests
- the team suggested that friends would be acceptable. Calin said he
would be happy to be in charge of recruiting volunteers.

Dan suggested the use of the proposed fitness devide in medical settings may add additional constraints on the hardware
and tools that can be used, as many warranties forbid such use. The team agreed this was essencial to keep in mind and adhere
to if possible.

\task{Emily}{Write up and chase ethics approval}
\decision*{Try to use only medical-approved hardware and tools}

\topic{Next Meeting}
Dan suggested meeting on Monday, Mohit proposed possibly Friday. Emily
agreed that those were the two most sensible dates and proposed that she
write up the brief and circulate it amounst the team in time for a
meeting on Monday. It could then be agreed upon, then sent to Dr Merrett
and Dr Weddell in good time to get their feedback. The team agreed.

\decision*{Hold next meeting at 3pm on Monday, 5th}

\end{Minutes}
\end{document}