\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage[letterpaper, margin=1in]{geometry}

\pagestyle{plain}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\begin{document}
\selectlanguage{english}

\begin{Minutes}{Team Meeting 3}
\participant{\
    Emily Shepherd, \
    Mohit Gupta, \
    Dan Playle, \
    Toby Finch}
\minutesdate{13 October 2015}
\starttime{19:00}
\endtime{19:30}
\location{Zepler Level 3 Labs}
\maketitle

\topic{Background Research}
Dan opened the meeting by stating that he had done some background research into various classification
algorithms using Waka to process some sample data which he had collected using an app on his phone. He
showed a graph with a recording of x, y and z measurments, as well as the absolute displacement at each
instant. He then demonstrated Waka's ability to process this data with any desired classification system.

\topic{Ethical Approval}
Toby went over the progess of the ethical approval, and stated that he and Emily had completed the required
forms. He noted, however that it may be sensible to push back the planned week as the ethical approval would
take longer than expected due to the requirement to get a first aid contact. Emily and Toby discussed this
for a short time, and agreed to push back the date of data collection back to week six.

\decision*{Move data collection group to week 6}

\topic{Hardware}
Mohit discussed the data sheets he had read so far - he noted that there were many variants of the Cortex M0,
each with different memory abilities. The group opted to select the device with the lowest memory capability.

Emily asked if there had been any progress made in researching whether the FPGA was required or not - Mohit
stated that they had not come to a clear decision on this.

\topic{Meeting with the Customer}
Toby stated that the time all members of the group were free was at 3pm so the meeting with the customer
would be then, he also said that Dr Weddell had offered to host the Southampton End of the skype call in
his office. Emily suggested brainstorming some questions to ask him:

The main issue that needed clarification was that of clock speed, as it was unclear if we would need to use
an FPGA for to clock the device at lower speeds. Emily also suggested that the team should ask would he
is looking for from the project, and Dan added that we could also ask how much he would like to be involved.

\topic{Project Goals}
Emily suggested talking about the project's goals, as Dr Weddell had been somewhat critical about the group's
progress so far. The team discussed various aspects of the design, specifically questioning how many sensors
would be required, and where exactly on the body these would need to go, concluding that the following
locations would be required:
\begin{itemize}
	\item On the foot
	\item The calf
	\item The upper leg
	\item The arm
\end{itemize}

\topic{Research}
Emily also suggested discussing the research that would be required. Dan stated that, as he had already made
progress at Machine Learning research, it would make sense for him to continue with this. Emily agreed and
said she would be happy to look at Machine Learning in constrained systems

\topic{Marks}
Dan stated that some other teams had been reading the marks scheme and ensuring that their work and progress
met all of the required criteria. He suggest creating agendas for meetings, as well as minutes - Emily agreed
with this. Dan also suggested using MoSCoW.

\task{Emily}{Create agendas for meetings}

\end{Minutes}

\end{document}