\documentclass{article}
\usepackage[english]{babel}
\usepackage{minutes}
\usepackage[letterpaper, margin=1in]{geometry}

\pagestyle{plain}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}

\begin{document}
\selectlanguage{english}

\begin{Minutes}{Initial Supervisor Meeting}
\participant{\
    Emily Shepherd, \
    Mohit Gupta, \
    Dan Playle, \
    Toby Finch, \
    Calin Pasat, \
    Dr Geoff Merrett, \
    Dr Alex Weddell}
\minutesdate{30 September 2015}
\starttime{15:00}
\endtime{16:00}
\location{59/4227}
\maketitle

\topic{Introduction}
Dr Merrett lead the meeting; he began by introducing himself and Dr
Weddell. He then went over the current proposal. He noted that it had
been primarily aimed at Electronic students, so there may need to be
changes made in light of the fact most of the team are Computer
Scientists, but he did not think this would be a problem. He also stated
that the project was aimed at a team of 4 and there might, therefore, be
room for extensions to the project as the team has 5 members.

After the project brief, Dr Merrett asked the team members what their
primary interests were. Emily began be stating that the team as a whole
had aimed for a Networking-related task. Each member of the team
concurred, Security also being mentioned by several members. Dr Merrett
stated that those interests would not be compatible with the brief, but
there was a general consensus that this would not be a problem going
forward.

Following from this, Dr Merrett asked if the team had any questions
about the brief, and ideas for how to proceed. Emily responded that his
description had been very good, and that there was scope in the project
to use both the Computer Scientists' and Electronic Engineers' skill sets.

\topic{Hardware}
Dr Weddell asked if the team were aware what an M0 was (this is referred
to in the Project Brief) - to which the general response was no. He then
explained that the Cortex M class processors are designed to work in
low-power systems and environments and that the M0 is the lowest in this
class. Dr Merrett gave a more general description of the concept of
reducing power at the cost of having to run the processor more slowly.

Dr Weddell stated that it would be sensible to use an under-clocked M0
for our project, to emulate the capability of the proposed ultra-low
power processor. Dr Merrett stated that we should acquire and FPGA Board
and a lab desk. Mohit and Calin confirmed they were able to do this, and
confirmed that a risk assessment would need to be carried out.

\task*{Acquire FPGA Board}
\task*{Complete Risk Assessment}
\task*{Acquire Lab Desk}

\topic{General GDP Discussion}
Dr Weddell pointed out that it would also be appropriate for the team to
inspect the mark scheme, to know what is best to focus on as a team, and
noted that team work and project management contributed to a large
proportion of the marks. Dr Merrett agreed with this, and explained
that, while it would be easy for him to tell if we worked well in a team
as he would be meeting us regularly, it would not be so obvious to our
second examiner. He advised us to take minutes of our meetings.

Dr Merrett then further advised the group to delegate tasks into sub-\
groups, and to nominate a leader, minute taker and budget holder. Dr
Weddell added that it was best for one member of the team to speak to
the company (ARM) so a Company Representative would also be sensible to
nominate. Dr Merrett reminded the group that, should they wish to use
subjects to collect data about body movement, ethical approval would be
required, and that this may take some times.

\task*{Take Formal Minutes of Meetings}
\task*{Nominate Leader}
\task*{Nominate Minute Taker}
\task*{Nominate Budget Holder}
\task*{Nominate Company Representative}
\task*{Investigate Ethics Approval}

\topic{Next Meeting}
Dr Merrett stated that the team should discuss the brief amongst
themselves, agreeing if it would require any extensions or, if the team
wanted to change anything, this would require negotiation. We then
discussed the time of recurring weekly meetings, agreeing that the best
time for everyone is 1pm on Thursdays.

\task*{Prepare counter-brief}
\task*{Meet at 1pm on Thursdays}

\end{Minutes}
\end{document}